Phonon polaritonics in two-dimensional materials

### 2019-03-18 paper.tex
discussion of 2.5D scenario

The third comment is that the considerations of this section can be extended to few-layer systems, such as hBN bilayers, which may still be considered 2D for polariton wavelengths large compared to the bilayer thickness. The considerations may also be extended to 1D polar materials, such as BN nanotubes. For bilayers, as was discussed in Ref.~\citenum{sohier2017breakdown}, one may describe the LO--TO splitting in terms of Eq.~\eqref{eq:zerosofresponse}, with the 2D Coulomb interaction, but with eigendisplacements appropriate to the few layer system. For a small number of layers $N$, this should enhance the LO--TO splitting by a factor of $N$. For 1D systems, beyond using the eigendisplacements appropriate to the 1D system, one must also use the 1D Coulomb interaction, cutoff by a length $R$ which for a nanotube, would be its radius. In that case, the 1D Coulomb interaction is $e^2K_0(qr)/2\pi\epsilon_0$, where $K_0$ is the (zeroth order) modified Bessel function of the second kind. Thus, the $q$-dependence of the LO--TO splitting is $q^2K_0(qR)$. This is in close analogy with the relation for the plasma frequency of 1D plasmons, as expected from the considerations of the previous paragraph. As regards the optical properties, the optical conductivity is still governed by Eq.~\eqref{eq:2dsusceptibility}.

%\textcolor{blue}{The third comment is that the considerations of this section can be extended to few-layer systems, such as hBN bilayers, which may still be considered 2D for polariton wavelengths large compared to the bilayer thickness. The considerations may also be extended to 1D polar materials, such as BN nanotubes. For bilayers, as was discussed in Ref.~ \cite{sohier2017breakdown}, one may describe the LO--TO splitting in terms of Eq. ~\ref{eq:zerosofresponse}, with the 2D Coulomb interaction, but with eigendisplacements appropriate to the few layer system. For a small number of layers $N$, this should enhance the LO--TO splitting by a factor of $N$. For 1D systems, beyond using the eigendisplacements appropriate to the 1D system, one must also use the 1D Coulomb interaction, cutoff by a length $R$ which for a nanotube, would be its radius. In that case, the 1D Coulomb interaction is $\frac{e^2K_0(qr)}{2\pi\epsilon_0}$, where $K_0$ is a modified Bessel function of the second kind and of order zero. Thus, the $q$-dependence of the LO--TO splitting is $q^2K_0(qR)$. This is in close analogy with the relation for the plasma frequency of 1D plasmons, as expected from the considerations of the previous paragraph. As regards the optical properties, the optical conductivity is still governed by Eq.~\ref{eq:2dsusceptibility}.}

>>>>

The third comment is that the considerations of this section can be extended to few-layer systems, such as hBN bilayers, which may still be considered 2D for polariton wavelengths large compared to the bilayer thickness. The considerations may also be extended to 1D polar materials, such as BN nanotubes. For bilayers, as was discussed in Ref.~\citenum{sohier2017breakdown}, one may describe the LO--TO splitting in terms of Eq.~\eqref{eq:zerosofresponse}, with the 2D Coulomb interaction, but with eigendisplacements appropriate to the few layer system. For a small number of layers $N$, this should enhance the LO--TO splitting by a factor of $N$. To go beyond an effectively 2D description of a monolayer, and make the transition from monolayer to bulk, we may make use of the "2.5D" Coulomb interaction \cite{thygesen2017calculating} in Eq.~\ref{eq:zerosofresponse}. In that case, for a film of thickness $d$, the interaction takes the form $V(q) = \frac{e^2}{\epsilon_0 dq^2}\left(1-\frac{2}{qd}e^{-\frac{qd}{2}}\sinh\left(\frac{qd}{2}\right) \right)$. This form interpolates between the 2D and 3D interactions in the limits $qd \rightarrow 0$ and $qd \rightarrow \infinity$. For sufficiently large thickness and finite-q, the 2.5D Coulomb interaction scales as $\frac{1}{dq^2}$. Noting the $q^2$ factor in Eq.~\ref{eq:zerosofresponse}, as well as the $N$-dependence of the quantity involving eigendisplacements, one finds an LO-TO splitting independent of thickness, as expected for bulk samples.

For 1D systems, beyond using the eigendisplacements appropriate to the 1D system, one must also use the 1D Coulomb interaction, cutoff by a length $R$ which for a nanotube, would be its radius. In that case, the 1D Coulomb interaction is $e^2K_0(qr)/2\pi\epsilon_0$, where $K_0$ is the (zeroth order) modified Bessel function of the second kind. Thus, the $q$-dependence of the LO--TO splitting is $q^2K_0(qR)$. This is in close analogy with the relation for the plasma frequency of 1D plasmons, as expected from the considerations of the previous paragraph. As regards the optical properties, the optical conductivity is still governed by Eq.~\eqref{eq:2dsusceptibility}.

%\textcolor{blue}{The third comment is that the considerations of this section can be extended to few-layer systems, such as hBN bilayers, which may still be considered 2D for polariton wavelengths large compared to the bilayer thickness. The considerations may also be extended to 1D polar materials, such as BN nanotubes. For bilayers, as was discussed in Ref.~ \cite{sohier2017breakdown}, one may describe the LO--TO splitting in terms of Eq. ~\ref{eq:zerosofresponse}, with the 2D Coulomb interaction, but with eigendisplacements appropriate to the few layer system. For a small number of layers $N$, this should enhance the LO--TO splitting by a factor of $N$. To go beyond an effectively 2D description of a monolayer, and make the transition from monolayer to bulk, we may make use of the "2.5D" Coulomb interaction \cite{thygesen2017calculating} in Eq.~\ref{eq:zerosofresponse}. In that case, for a film of thickness $d$, the interaction takes the form $V(q) = \frac{e^2}{\epsilon_0 dq^2}\left(1-\frac{2}{qd}e^{-\frac{qd}{2}}\sinh\left(\frac{qd}{2}\right) \right)$. This form interpolates between the 2D and 3D interactions in the limits $qd \rightarrow 0$ and $qd \rightarrow \infinity$. For sufficiently large thickness and finite-q, the 2.5D Coulomb interaction scales as $\frac{1}{dq^2}$. Noting the $q^2$ factor in Eq.~\ref{eq:zerosofresponse}, as well as the $N$-dependence of the quantity involving eigendisplacements, one finds an LO-TO splitting independent of thickness, as expected for bulk samples.}

% \textcolor{blue}{For 1D systems, beyond using the eigendisplacements appropriate to the 1D system, one must also use the 1D Coulomb interaction, cutoff by a length $R$ which for a nanotube, would be its radius. In that case, the 1D Coulomb interaction is $\frac{e^2K_0(qr)}{2\pi\epsilon_0}$, where $K_0$ is a modified Bessel function of the second kind and of order zero. Thus, the $q$-dependence of the LO--TO splitting is $q^2K_0(qR)$. This is in close analogy with the relation for the plasma frequency of 1D plasmons, as expected from the considerations of the previous paragraph. As regards the optical properties, the optical conductivity is still governed by Eq.~\ref{eq:2dsusceptibility}.}
